\section*{Introduction}
Although maize is naturally an out-crossing organism, modern breeding develops highly inbred lines that are then used in controlled crosses to produce hybrids. Hybrid maize has been so successful that it quickly replaced long-standing mass-selected open pollinated varieties (Crabb, 1947). 
Maize inbred lines are now partitioned into separate inbreeding ‘heterotic groups’ that maximize performance and hybrid vigor (heterosis) when an inbred line of one group is crossed with the other group (Tracy and Chandler, 2006). 
The shift towards selection of inbred lines based on their ability to generate good hybrids – referred to as ‘combining ability’ – constituted an abrupt change from the open-pollinated mass selection that breeders practiced for millennia (Anderson, 1944; Troyer, 1999).
Multiple studies with molecular markers have indicated that the modern era of single-cross hybrid maize breeding has led to a dramatic restructuring of population genetic variation (Duvick et al., 2004; Ho et al., 2005; Feng et al., 2006). 
Different heterotic groups have diverged genetically over time to become highly structured and isolated populations. 
Advances in high throughput genotyping and the development of a maize reference genome now enable the observation of maize population structure at high marker density across the whole genome \citep{ganal2011a-large,chia2012maize}. 
So far, these high-density studies have examined a broad spectrum of germplasm at various points in the history of maize to search for the signals of population structure and artificial selection \citep{Hufford2012b, van2012historical}. 
Although selective sweeps remaining from domestication are clearly visible, the impact of selection during modern breeding appears comparatively small in terms of its impact on genomic diversity despite steady, heritable improvement in phenotype (Duvick, 2005). 
The lack of distinct selection signals from modern breeding may be due to specific selective events occurring in different populations, necessitating a more focused look within heterotic groups or even single breeding programs. 
In this study, we apply a genomic approach to study the dynamics of genetic variation over time within an individual selection experiment. 
The Iowa Stiff Stalk Synthetic (BSSS) and the Iowa Corn Borer Synthetic No. 1 (BSCB1) Reciprocal Recurrent Selection Program of the USDA-ARS at Ames, Iowa (hereafter referred to as the Iowa RRS) represents one of the best-documented public experiments on selection for combining ability and hybrid performance. 
BSSS and BSCB1 have been recurrently selected for improved cross-population hybrids (Penny and Eberhart, 1971). 
This model of selection, named reciprocal recurrent selection, provides the generalized model for strategies used in commercial maize breeding (Comstock et al., 1949; Duvick et al., 2004). 
The Iowa RRS experiment proves especially relevant because lines derived from the BSSS population have had a major impact upon the development of commercial hybrids (Duvick et al., 2004; Darrah and Zuber, 1986), the formation of modern heterotic groups (Troyer, 1999; Senior et al., 1998), and the choice of a maize reference genome \citep{schnable2009the-b73-maize}.